---
title: "S040 Unit 1 Quiz"
author: "Julia English"
date: "2022-09-12"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r loading libraries and data}
rm(list = ls())
library(foreign)
library(dplyr)
library(ggplot2)

library(foreign)
setwd("C:/Data Files")
wvs <- read.dta('C:/Data Files/wvs_class (1).dta')


my_tab_haiti <- wvs %>% filter(country == "Haiti") %>% select(justifiable_abortion_simple, believe_in_god) %>%
  table()

my_tab_haiti

my_tab_haiti_prop <- my_tab_haiti %>% prop.table(margin = 2) %>% round(digit = 2)

my_tab_haiti_prop

test_haiti <- chisq.test(my_tab_haiti)

test_haiti



 

```
/chi^2(df = 1) = 0.0164, p = 0.8981
 The null hypothesis would be that there is no association between believing in god and finding abortion justifiable in the Haitian population. We cannot reject the null hypothesis because the probability of reaching this observed value is not small enough compared to the sampling distribution of the test statistic under the null hypothesis. There is not enough evidence to support a relationship between a belief in god and believing that abortion is justifiable in the Haitian population.
 
```{r japan}
my_tab_japan <- wvs %>% filter(country == "Japan") %>% select(justifiable_abortion_simple, believe_in_god) %>%
  table()

my_tab_japan

my_tab_japan_prop <- my_tab_japan %>% prop.table(margin = 2) %>% round(digit = 2)

my_tab_japan_prop

test_japan <- chisq.test(my_tab_japan)

test_japan
```
 
/chi^2(df = 1) = 1.1336, p = 0.287
The null hypothesis would be that there is no association between believing in god and finding abortion justifiable in the Japanese population. We cannot reject the null hypothesis because the probability of reaching this observed value is not small enough compared to the sampling distribution of the test statistic under the null hypothesis. There is not enough evidence to support a relationship between a belief in god and believing that abortion is justifiable in the Japanese population..
